\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-23 k-planar.tex
Made a table

@@

\subsection{Outline}

The remainder of this paper is organized as follows: 
\begin{compactitem}
  \item In \cref{Structure} we prove our main result for shortcut systems (\cref{ShortcutProduct}), and its optimisations for $k$-planar graphs and their genus-$g$ generalisation (\cref{kPlanarProduct,gkPlanarProduct}).  
  \item \Cref{examples} uses \cref{Structure} to derive product structure theorems for string graphs, powers of bounded-degree graphs, and $k$-nearest neighbour graphs.
  \item \Cref{FramedSection} proves a product structure theorem for $d$-framed multigraphs in which the graph $H$ has treewidth $3$ and is planar.  Using this result, we derive product structure theorems for $1$-planar graphs and map graphs, again with a planar graph $H$.  
  \item \Cref{Applications} quickly surveys applications of product structure and the consequences of the current work.  
  \item \cref{WrappingUp} concludes with an open problem.
\end{compactitem}

@@

\begin{thm}
  Every $k$-nearest neighbour graph is a subgraph of $H\boxtimes P\boxtimes K_{\ell}$ for some graph $H$ of treewidth $O(k^6)$ and some $\ell\in O(k^4)$.
\end{thm}

>>>>

\note{PM}{Move this section out of the introduction, into a ``preliminaries'' section?}

@@

\subsection{Overview and Outline}

\cref{summary_table} summarizes existing results on product structure theorems for minor-closed graph classes and new results for non-minor-closed graph classes.  The remainder of this paper is organized as follows:

\begin{table}
  \begin{center}
    \begin{tabular}{lccl}
      \textbf{Graph class} & \boldmath $\tw(H)$ & \boldmath $\ell$ & \textbf{Ref.} \\ \hline\hline
      Planar & $3^*$ & $3$ & \cite{DJMMUW20} \\
      Planar & $6^*$ & $1$ & \cite{UWY} \\
      Genus-$g$ & $3^*$ & $\max\{2g,3\}$ & \cite{DHHW} \\
      Genus-$g$ & $2g+6$ & 1 & \cite{UWY} \\
      Apex-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\[1ex]
      % B-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      $k$-planar & $\binom{k+4}{3}-1$ & $18k^2 + 48k + 30$ & \cref{kPlanarProduct} \\
      $(g,k)$-planar & $\binom{k+4}{3}-1$ & $\max\{2g,3\}(6k^2+16k+10)$ & \cref{gkPlanarProduct} \\
      $(g,\delta)$-string & $\binom{\delta+4}{3}-1$ & $\max\{2g,3\}(\delta^4 + 4\delta^3 + 9\delta^2 + 10\delta+4)$ & \cref{StringPartition} \\
      $k$-NN & $O(k^6)$ & $O(k^4)$ & \cref{nn_product_structure} \\
      $d$-framed & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{d_framed_product_stucture} \\
      $1$-planar & $3^*$ & $7$ & \cref{1_planar_product} \\
      $d$-map & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{NewMapGraph} \\
      $(g,d)$-map & $\textcolor{red}{?}$ & $\textcolor{red}{?}$ & \textcolor{red}{\cref{NewMapGraph}} \\ \hline
      \\[.2ex]
      \multicolumn{4}{l}{$^*$ the bound also applies to the simple treewidth of $H$.}
    \end{tabular}
  \end{center}
  \caption{Summary of known product structure theorems.}
  \label{summary_table}
\end{table}

\begin{compactitem}
  \item In \cref{Structure} we prove our main result for shortcut systems (\cref{ShortcutProduct}), and its optimisations for $k$-planar graphs and their genus-$g$ generalisation (\cref{kPlanarProduct,gkPlanarProduct}).
  \item \Cref{examples} uses \cref{Structure} to derive product structure theorems for string graphs, powers of bounded-degree graphs, and $k$-nearest neighbour graphs.
  \item \Cref{FramedSection} proves a product structure theorem for $d$-framed multigraphs in which the graph $H$ has treewidth $3$ and is planar.  Using this result, we derive product structure theorems for $1$-planar graphs and map graphs, again with a planar graph $H$.
  \item \Cref{Applications} quickly surveys applications of product structure and the consequences of the current work.
  \item \cref{WrappingUp} concludes with an open problem.
\end{compactitem}

@@

\begin{thm}\label{nn_product_structure}
  Every $k$-nearest neighbour graph is a subgraph of $H\boxtimes P\boxtimes K_{\ell}$ for some graph $H$ of treewidth $O(k^6)$ and some $\ell\in O(k^4)$.
\end{thm}
